Learning action models with minimal observability

### 2018-12-21 doc/aij18/major-revision/experiments.tex
Sentence Madagascar changed

\item {\bf Planner}. The classical planner we used to solve the instances of $P_\Lambda$ that result from our compilations is {\sc Madagascar}~\cite{rintanen2014madagascar}. We used {\sc Madagascar} for two reasons:

  \begin{enumerate}
  \item  its ability to deal with planning instances populated with dead-ends~\cite{lopez2015deterministic}.
  \item  its ability to leverage the horizon of the solution plan when it is known. Specifically, when the length of the plan traces is known; i.e., \FO action sequences or \FO state trajectories, the horizon of the solution plan is also known, and this can be exploited by a SAT-based planner like MADAGASCAR. SAT-based planners are able to apply the actions for programming preconditions in parallel in a single planning step (and the same for the actions programming the effects) since these actions do not interact. Hence, we also know that the programming of the prefix of a solution plan is solvable in two steps, independently of the number of programming actions applied.
  \end{enumerate}

>>>>

\item {\bf Planner}. The classical planner we used to solve the instances of $P_\Lambda$ that result from our compilations is {\sc Madagascar}~\cite{rintanen2014madagascar}. We used {\sc Madagascar} for several reasons:

  \begin{enumerate}
  \item \textcolor[rgb]{1.00,0.00,0.00}{Other planners such as {\sc FastDownward} were also tested but provided worse experimental results}
  \item \textcolor[rgb]{1.00,0.00,0.00}{A SAT-based planner like {\sc Madagascar} is particularly suitable for tasks where the observed plan trace $\tau$ determines the horizon of the solution plan (case 1 presented in section \ref{task_definition})}. In this case, the prefix of the solution plan is solvable in two steps because the actions for programming preconditions can be applied in parallel in a single step and the same for the actions programming the effects.
  \item \textcolor[rgb]{1.00,0.00,0.00}{When the horizon of the plan is unknown (case 2 presented in section \ref{task_definition}), the ability of {\sc Madagascar} to deal with instances populated with dead-ends is very helpful~\cite{lopez2015deterministic}.}
  \end{enumerate}
